### 2016-05-01 definitions.tex
Fixed first 4 sections

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern, $\mathbb{T} = \{1,2,...,m\}$ be the descritized sequence of timestamps. We use $T[i]$ to denote the $i^{th}$ entry in a time sequence.

Given a time sequence $T \subseteq \mathbb{T}$, let $|T|$ be the cardinality of the sequence. We say a sequence $T$ is \emph{(fully)consecutive}
if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

\begin{definition}[$L$-consecutive]
A time sequence $T$ is $L$-consecutive iff $\forall$ its maximal consecutive subsequences $T^m$, $|T^m| \geq L$.
\end{definition}

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is not $3$-consecutive since $\{5,6\}$ is a maximally consecutive subsequence with cardinality less than $3$. $T$ is $2$-consecutive since both its two maximally consecutive subsequences are of the sizes greater or equal to $2$. It is notable that, for a sequence $T$, all its maximally consecutive subsequences are non-overlapping.

We then define the $G$-separateness as follows:

\begin{definition}[$G$-separated]
A time sequence $T$ is $G$-separated iff $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$
\end{definition}

Take $T={1,2,3,5,6}$ as an example. $T$ is $2$-separated since the gap between its maximally consecutive subsequnces is $5-3=2$. However, $T$ is not $1$-separated. Indeed, $1$-separated infers that $T$ is fully consecutive.

Given a time sequence $t$, objects locations at $t$ collectively forms a \emph{snapshot}\footnote{Missing timestamps can be interpreted using linear interpolation~\cite{jeung2008convoy}}.Objects in a snapshot can thus be clustered based on the
closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, we can then define the generalized co-moving pattern as follows:

\begin{definition}[Generalized Co-Movement Pattern]
A \emph{generalized co-movement pattern} $GCMP(M,K,L,G)= \langle O,T \rangle$ is a pair containing an object set $O\subseteq \mathbb{O}$ and a sequence $T \subseteq \mathbb{T}$, with the following constraints:
\begin{enumerate}
\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
\item{Significance: $|O| \geq M$}
\item{Duration: $|T| \geq K$}
\item{Consecutiveness: $T$ is $L$-consecutive}
\item{Separateness: $T$ is $G$-separated}
\end{enumerate} 
\end{definition}

The generalized co-movement pattern retains the patterns that discovered by existing techniques (convoy, swarm and platoon). In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} pattern. In addition to covering existing patterns, the generalized co-movement pattern avoids the \emph{miss-pattern} problem in \emph{platoon} pattern. As suggested in Figure~\ref{fig:platoon_weakpoint}, $\{100,101\}$ will be included in the platoon pattern, however since they're too far away in temporal domain, this pattern is not prominent. By setting appropriate $G$, we are able to prune these two snapshots. Notice that such a new pattern cannot be modeled by existing patterns.

It is notable that the number of patterns in GCMP is exponential. To control the number of output patterns, we noticed that, for two pattern result $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern. Based on this observation, we define the \emph{closed generalized co-movement pattern} as follows:
\begin{definition}[Closed Generalized Co-moving Pattern]
A generalized co-moving pattern $P=\langle O, T \rangle$ is a closed generalized co-moving pattern if and only if there does not exists another generalized co-moving pattern $P'$ s.t. $P'.O \supseteq P.O$.
\end{definition}
For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_1,o_2\}\{1,2,3,4\}$ is not a closed pattern, while $\{o_1,o_2,o_3\}$ $\{1,2,3,4\}$ is a closed pattern.The closed pattern avoids to output duplicate information, thus making the result patterns more compact. 
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

Although the generalized co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting objects with arbitrary spatio-shaped clusters. Therefore in this paper, we mainly consider density-based clustering.

The goal of this paper is to present a parallel solution for discovering GCMP from large-scale trajectory data.

@@

\begin{table}
\begin{tabular}{|c|c|}
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline 
$\mathbb{T}$ & Global time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}

>>>>

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ denote the set of objects in concern. 
We use $T \subseteq \{1,2,...,m\}$ to denote a descritized sequence of timestamps, where
$T[i]$ denotes the $i^{th}$ entry in the sequence and $|T|$ is the 
cardinality of the sequence.

A time sequence is consecutive if the difference between any of its neighboring entries
is 1, that is $\forall T[i], T[i+1] \in T, T[i+1] = T[i] + 1$. For any time sequence,
it can be decomposed into at least one consecutive portion(s). Therefore we can define the 
$L$-consecutiveness as follows:
%
%
%We say a sequence $T$ is \emph{(fully)consecutive}
%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
has cardinality greater or equal to $L$.
\end{definition}

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is not $3$-consecutive since $\{5,6\}$ has a cardinality less than $3$. $T$ is $2$-consecutive since both of its consecutive portions are of sizes at least $2$.
To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows:

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
 $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$.
\end{definition}

Take $T=\{1,2,3,5,6\}$ as an example. $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. However, $T$ is not $1$-connected. Indeed, $1$-connection infers that $T$ is consecutive.

Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the
closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
\begin{definition}[General Co-Movement Pattern]
A \emph{General co-movement pattern} $GCMP(M,K,L,G)= \langle O,T \rangle$ is a pair containing an object set $O\subseteq \mathbb{O}$ and a time sequence $T$, with the following constraints: (1)Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$. (2) Significance: $|O| \geq M$. (3) Duration: $|T| \geq K$. (4) Consecutiveness: $T$ is $L$-consecutive, and (5)Connection: $T$ is $G$-connected.
%\begin{enumerate}
%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
%\item{Significance: $|O| \geq M$}
%\item{Duration: $|T| \geq K$}
%\item{Consecutiveness: $T$ is $L$-consecutive}
%\item{Separateness: $T$ is $G$-separated}
%\end{enumerate} 
\end{definition}

The general co-movement pattern retains the patterns that discovered by all 
existing techniques (group, flock, convoy, swarm and platoon). 
The relationships between general co-movement pattern and other patterns are summarized in Table~\ref{tbl:patterns}.
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Pattern & $L$ & $G$ & $M$ & $K$ \\ 
\hline
Group & $\cdot$ & $|T|$ & $2$ & $1$ \\
\hline
Flock & $K$ & 1 & $\cdot$ & $\cdot$ \\
\hline 
Convoy & $K$ & $1$ & $\cdot$ & $\cdot$\\ 
\hline 
Swarm & $1$ & $|T|$ & $\cdot$ & $\cdot$ \\ 
\hline 
Platoon & $\cdot$ & $|T|$ & $\cdot$ & $\cdot$\\ 
\hline 
\end{tabular} 
\caption{Representing other patterns using GCMP. $\cdot$ means user specified value.}
\label{tbl:patterns}
\end{table}

In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern. 
In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent. By setting appropriate $G$, we are able to prune this anomaly. It is notable that GCMP is not able to be modeled by existing patterns.

It is also observable that the number of patterns in GCMP is exponential. To control the size of output, 
we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern. Therefore, we can define the \emph{Closed General Co-Movement Pattern} as follows:

\begin{definition}[Closed General Co-Movement Pattern]
A general co-moving pattern $P=\langle O, T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
\end{definition}

For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_1,o_2\}\{1,2,3,4\}$ is not a closed pattern, while $\{o_1,o_2,o_3\}$ $\{1,2,3,4\}$ is a closed pattern. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.

LETS KEEP THE CLOSENESS INFORMATION AT THE MOMENT. IF NO CLOSENESS IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes. Therefore in this paper, we mainly consider density-based clustering.
Our definition of GCMP is free from clustering method. Users are able to supply different clustering method to facilitate different needs. We currently expose both disk-region based clustering and DBSCAN as APIs to the user.

In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory data.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|} 
\hline
Symbols & Meanings \\
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline 
$T$ & Time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}

### 2016-05-01 system.tex
Fixed first 4 sections

\section{Preliminary on Apache Spark}
Apache Spark is an open sourced modern parallel processing platform
based on Resilient-Distributed-Dataset (RDD). Each RDD is able to take an action (including Map, Reduce, GroupByKey etc.) and then transforms to a new RDD. Algorithms in Spark is implemented by supplying various actions to an input RDD. Each RDD in Spark has a pre-defined and fixed number of partitions, where each partition forms a task assigned to an executor.

Compared to MapReduce, Spark 
utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}. In order to fully utilize the memory, Spark creates one thread for each task and then multiple tasks belonging to the same JVM share the available memory.
Due to threading, there is a paradigm shift from MapReduce to Spark. In MapReduce, the cost of starting a task is expensive, as each task in MapReduce requires a dedicated JVM process. While in Spark, the cost of starting a task is negligible since each task is done by a thread.  Therefore in Spark, we may create many more parallel tasks than in MapReduce before reaching to the system limitation.

\section{Mining Generalized Co-moving Pattern}
There are two stages in mining GCMP. The first stage is to cluster objects in each snapshots. Then the seconds stage is to mine patterns from clusters in parallel. The overview of the parallel approach is 
shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
read trajectories and cluster objects in the same snapshots. Since the objects at each snapshots are independent, this stage can be easily performed in parallel. The first stage involves network IO. Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.
In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.

\begin{definition}[Completeness and Soundness]
Let a partitioning method $\mathbb{P}$ partitions original trajectories $TR$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $TR$, $\exists Par_i$ such that $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
\end{definition}
The completeness ensures that no real patterns are missed out. The soundness ensures that no false patterns are reported. If a partition method is both sound and complete, we are then able to mining patterns in each resulted partition in parallel.

Depends on the pattern mining strategy, the size of shuffle and replication may differ. We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.

\begin{figure} [h]
\center
\includegraphics[width=0.5\textwidth]{system_layout.jpg}
\caption{System Flow of Mining GCMP}
\label{fig:overview}
\end{figure}

\subsection{Temporal Replication and Mining}
The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
A simple but effective method
is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
some of the snapshots need to be replicated on multiple executors.
We call this method the \emph{Temporal Replication and Mining} approach. 
The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.

>>>>

\section{Overview of Mining GCMP in Parallel}
\label{sec:system_overview}
We adapt the MapReduce paradigm for designing
a parallel solution of mining GCMP. MapReduce was proposed by Dean et. cl.~\cite{}
and has become a mature parallel platform for large-scaled data processing. 
Current open source MapReduce systems provide handy programming APIs with fault tolerances
in backends. Such systems 
include Apache Hadoop, Apache Shark and Apache Spark to name a few.

In simple words, there are two types of cluster nodes in MapReduce, namely the 
\emph{mapper}s and the \emph{reducer}s. The execution of a MapReduce task consists of
three stages: First, input data
are partitioned and read by a \emph{map} function on each mapper. Then, mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Finally,
reducers process received data using a \emph{reduce} function then write the
outputs.
Since the \emph{shuffle} stage needs to transfer data over network, 
an important attention to pay during designing MapReduce algorithms is 
to minimize the shuffle amounts and shuffle counts.

Our GCMP mining workflow follows the MapReduce style which consists of five stages
as illustrated in the Figures~\ref{fig:overview} (a)-(e).
As shown, in stage (a), trajectory data 
are read from various sources and partitioned based on objects timestamps, where objects
of the same timestamps form a snapshots. After partitioning, snapshots are send to workers
prior to stage (b). In stage (b), objects belonging to the same snapshots are clustered
based on the user supplied clustering method. Then those clusters are shuffled to 
workers prior to stage (c). In stage (c), each worker collects the clusters sent to its partition
and discover the GCMP from these local clusters. A post-check is required to remove
duplicate patterns. In stage (d), patterns discovered in previous stages are write to output.

\begin{figure} [t]
\center
\includegraphics[width=0.5\textwidth]{system_layout.eps}
\caption{System Flow of Mining GCMP}
\label{fig:overview}
\end{figure}

The first two stages of our solution could be straightforward. 
However, it is challenging to design the partition and mining methods
to in stage (c) and (d). Intuitively, A reasonable partition strategy 
needs to meet the following requirements: first, the result partitions need
to preserve enough information so that real patterns can be discovered
in stage (d). Second, the result partitions need to ensure that
the patterns that discovered in stage (d) are real patterns so that
no further validation is required after stage (d). We formalize the two 
properties using \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ such that $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
\end{definition}
The completeness ensures that no real patterns are missed out. The soundness ensures that no false patterns are reported. If a partition method is both sound and complete, we are then able to mining patterns in each resulted partition in parallel in stage (d).

Apparently replicating entire data set to each partition meets the \emph{soundness} and \emph{completeness}, however, it burdens the network shuffle and GCMP mining. Our objective is thus to design a complete and sound partition method that
minimize the network shuffles.

%Depends on the pattern mining strategy, the size of shuffle and replication may differ. We show that if the pattern mining strategy is not selected carefully, the second stage will suffer from large data replication and shuffling.

%
%In particular, we need
%the number of partitions to be reasonably large in order to achieve
%good parallelism in stage (d). Meanwhile, we need to ensure a partition 
%of snapshots containing enough information so that patterns discovered 
%in stage (d) are complete.  Furthermore, we have to ensure that the
%patterns that discovered in stage (d) are real patterns.

%However, there are two conflicting requirements that restrain us from 
%designing a simple and effective solution. 
%On one hand, we need to partition snapshots in stage (c) as many as possible 
%so that good parallelism could be achieved in stage (d). 
%On the other hand, in stage (d), 
%we require each partition containing enough information in order to discover
%proper GCMP patterns. This prevents us from arbitrarily partition snapshots in
%stage (d). To design a working algorithm, find the minimum size of partition is
%crucial. In the following section, we first design a naive approach that
%partitions snapshots by allowing overlapping among partitions. Such a partition strategy
%although has overhead in shuffling, it corrects find GCMPs in parallel in stage (d).
%In order to discover all patterns, we require a partitioning method to be \emph{complete} and \emph{Sound}.

%\section{Temporal Replication and Mining}
%
%
%%It is notable that some patterns 
%%may be very long in duration (e.g., when discovering \emph{swarm}) or some patterns 
%%may contain a large set of objects (e.g., when discover \emph{group} patterns with small $L$).
%%Therefore, we require the size of partition to be large enough. Reaching the
%%balance between the two requirement is crucial. In the following sections, we will
%%describe a naive partition scheme which meets the two requirements.
%
%%Our parallel solution incurs two rounds of shuffles. The first round of shuffle happens in step (a). This
%%is because that the trajectories stored in HDFS needs to be regrouped to form snapshots. 
%%The second round of shuffle occurs in step(d). This is because that 
%% the clusters need to be regrouped so that subsequent pattern detection can be performed.
%% Despite the simpleness of our parallel solution, it is actually nontrivial to work out a scalable solution.
%% The major challenge lies in the step (d) and (e). 
%
%
%%\section{Preliminary on Apache Spark}
%%\label{sec:system_overview}
%%Apache Spark is an open sourced modern parallel processing platform
%%based on Resilient-Distributed-Dataset (RDD). Each RDD is able to take an action (including Map, Reduce, GroupByKey etc.) and then transforms to a new RDD. Algorithms in Spark is implemented by supplying various actions to an input RDD. Each RDD in Spark has a pre-defined and fixed number of partitions, where each partition forms a task assigned to an executor.
%%
%%Compared to MapReduce, Spark 
%%utilizes distributed memory to cache the programming data modeled as RDDs, which brings computational benefits~\cite{shi2015clash}. In order to fully utilize the memory, Spark creates one thread for each task and then multiple tasks belonging to the same JVM share the available memory.
%Due to threading, there is a paradigm shift from MapReduce to Spark. In MapReduce, the cost of starting a task is expensive, as each task in MapReduce requires a dedicated JVM process. While in Spark, the cost of starting a task is negligible since each task is done by a thread.  Therefore in Spark, we may create many more parallel tasks than in MapReduce before reaching to the system limitation.

%\section{Mining Generalized Co-moving Pattern}
%\label{sec:solution}
%There are two stages in mining GCMP. The first stage is to cluster objects in each snapshots. Then the seconds stage is to mine patterns from clusters in parallel. The overview of the parallel approach is 
%shown in Figure~\ref{fig:overview}. As shown, trajectory data is initially stored in HDFS. The first stage is to 
%read trajectories and cluster objects in the same snapshots. Since the objects at each snapshots are independent, this stage can be easily performed in parallel. The first stage involves network IO. Afterwards, the clusters in each snapshots are shuffled and replicated to make various partitions.

\section{Temporal Replication and Mining}
The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
A simple but effective method
is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
some of the snapshots need to be replicated on multiple executors.
We call this method the \emph{Temporal Replication and Mining} approach. 
The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.
